Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-02 MultipleRoundSims/sections/06-results2.tex
typo

We observe that the behavior of both \Minerva audits is similar, and that the plot for SO \BRAVO is to the right (more ballots) and below (lower probability of stopping) those for \Minerva, even for a stopping probability as low as $0.25$. We observe that the plot for EoR \BRAVO shows the worst performance, which is not surprising. We observe similar behavior across margins (see Figures \ref{fig:missouri_25} and \ref{fig:mass_25}), though the improvement due to \Minerva reduces as margins get larger. We see also that the improvement due to using \Minerva is not as large as that seen for $S_1=0.9$ (see Figure \ref{fig:texas_90}).

>>>>

We observe that the behavior of both \Minerva audits is similar, and that the plot for SO \BRAVO is to the right of (more ballots) and below (lower probability of stopping) those for \Minerva, even for a stopping probability as low as $0.25$. We observe that the plot for EoR \BRAVO shows the worst performance, which is not surprising. We observe similar behavior across margins (see Figures \ref{fig:missouri_25} and \ref{fig:mass_25}), though the improvement due to \Minerva reduces as margins get larger. We see also that the improvement due to using \Minerva is not as large as that seen for $S_1=0.9$ (see Figure \ref{fig:texas_90}).
